\LARGE \bf Energy-Aware Dynamic Mission Planning Algorithm for UAVs

### 2020-10-14 icra-2021.tex
fixing text

%% math package
\usepackage[cmex10]{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{arydshln}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}

@@

\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{assm}[thm]{Assumption}
\newtheorem{cor}{Corollary}
\newtheorem{conj}{Conjecture}[section]
\newtheorem{defn}{Definition}[section]
\newtheorem{exmp}{Example}[section]
\newtheorem{rem}{Remark}

@@

The proposed algorithm alters the energy consumption dynamically by means of mission-specific parameters: the Quality of Service (QoS) values of the onboard computations, and the trajectory-explicit equations (TEEs) adjustments of the motion plan. Our goal is a mission extension by optimizing both QoS and TEEs parameters as the UAV flies and its batteries drain. The algorithm optimizes QoS requiring the UAV to include robot operating system (ROS) nodes. It optimizes TEEs--an abstraction of the trajectory--and guides the UAV using a vector field~\cite{de2017guidance} that converges smoothly to such trajectory. It relies on the assumptions of the mission being \emph{periodic} and \emph{uncertain}. The periodicity is directly observed, by e.g., the UAV flying in repetitive patterns, and the uncertainty accounts for the environmental interference with e.g., a fixed-wing UAV drifting due to windy weather. It addresses the periodicity modeling the energy with Fourier analysis--being the mission periodic, we expect the energy to evolve also periodically--and the uncertainty with a state estimator. It selects the controls (QoS and TEEs parameters) using robust output feedback model predictive control (MPC).

In the spirit of reducing waste, costs, and resources, we showcase the algorithm using the problem of dynamic mission planning for a precision agriculture fixed-wing UAV. Such a scenario is often put into practice~\cite{hajjaj2014review} with ground mobile robots used for harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, and UAVs for preventing damage and ensuring better crop quality~\cite{puri2017agriculture, daponte2019review}. The mission consist of a UAV flying in ellipses shifted in time, detecting obstacles using a convolutional neural network (CNN), and informing grounded mobile robots employed for future harvesting--a monitoring mission optimized for the craft's dynamics. The algorithm plans the mission controlling the processing rate and the length of the semi-major and -minor axis.  Data indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest QoS.

The remainder of the paper is organized as follows. The overview of dynamic mission planning is set in Section~\ref{sec:prob}, along with a suitable model for the position and energy. The algorithm that uses the model and solves the dynamic mission planning problem is proposed in Section~\ref{sec:algo}. Section~\ref{sec:experimental} presents the result and showcase the performance. The paper finishes with some conclusions in Section~\ref{sec:conclusion}.

@@

Let the mission be defined by a generic continuous twice differentiable TEE $\varphi$ and a set of $\sigma$ tasks. Moreover, let $t_f$ be the mission final time, $[\,\cdot\,]$ the set $\{1,2,\dots,\,\cdot\,\}$, and $\underline{\,\cdot\,},\overline{\,\cdot\,}$ the upper and lower bound of $\,\cdot\,$. At a time instant $k\in[0,t_f)\subseteq\mathbb{R}_{\geq 0}$, the mission is formally defined as the ordered list
\begin{equation}\label{eq:mission}\begin{split}
  \mathcal{M}_k:=\{(\varphi,\psi_1,...,\psi_\sigma)\mid\exists&\,\,\varphi\in\mathbb{C}_k,\,\\&\psi_i\in\mathbb{S}_{k,i}\,\forall i\in[\sigma]\},
\end{split}\end{equation}
where $\mathbb{C}_k:=[\underline{c}_k,\overline{c}_k]\subseteq\mathbb{R}$ is the TEE $\varphi$ adjustments constraints set, and $\mathbb{S}_{k,i}:=[\underline{\text{QoS}}_{k,i},\overline{\text{QoS}}_{k,i}]\subseteq\mathbb{Z}_{\geq 0}$ the $i$-th task QoS value constraints set.

The overall plan is the union of all the missions. If for simplicity the system is sampled discrete-time
\begin{equation}
  \mathcal{M}:=\bigcup_{i\in[tf]}{\mathcal{M}_i},
\end{equation}
the algorithm inputs $\mathcal{M}$ and outputs the position and the instantaneous energy consumption, while it adapts the control in function of the TEE and QoS parameters--an action performed evolving the mission state.

@@

Consider the position $\mathbf{p}\in\mathbb{R}^2$ of a UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ w.r.t. some inertial navigation frame $\mathcal{O}_W$, the set
\begin{equation}\label{eq:area}
  \mathcal{P}_k:=\{\mathbf{p}\mid\varphi_k(\mathbf{p},c_{k,1},\dots,c_{k,\rho})\in\mathbb{C}_k\},
\end{equation}
delimits the area where the $k$-th TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\rho}\rightarrow\mathbb{R}$ is free to evolve using $\rho$ controls $\mathbf{c}_k:=c_{k,1},...,c_{k,\rho}$ (TEEs adjustments), being such function satisfied for all the approaching points.

The algorithm uses the concept to select $\varphi_k(\mathbf{p},\mathbf{c}_k^0)$ with the highest energy value under the constraints. It guides the UAV to the new position deriving the direction to follow using the vector field of $\varPhi:=\varphi_k(\mathbf{p},\mathbf{c}_k^0)$. Such direction can be expressed as the desired velocity vector
\begin{equation}\label{eq:pd}
  \dot{\mathbf{p}}_d(\mathbf{p}):=E\nabla\varPhi-k_e\varPhi\nabla\varPhi,\,\,\,E=\begin{bmatrix}
    0&1\\-1&0
  \end{bmatrix},
\end{equation}
where $\nabla\varPhi\in\mathbb{R}^2$ is the gradient, $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence. The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the atmospheric interference.

The algorithm models the energy using a state $\mathbf{q}\in\mathbb{R}^j$ derived from Fourier analysis (the meaning of $j$ is clarified to the reader in the next subsection) and decompose such evolution in the energy due to the trajectory, and computations--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.

@@

Suppose no uncertainty in the form of $\mathbf{w}_k\in\mathbb{R}^j,v_k\in\mathbb{R}$ accounting otherwise for the unknown state and output is present. The non-linear model in Equation~(\ref{eq:fourier}) can be expressed using an equivalent linear discrete time-invariant state-space model
\begin{equation}\label{eq:state-perf}\begin{cases}
  \mathbf{q}_{k+1}&=A\mathbf{q}_{k}+B\mathbf{u}_{k}+\mathbf{w}_k\\
  y_k&=C\mathbf{q}_k+v_k
\end{cases},\end{equation}
where $y_k\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption. We prove formally in the Theorem~\ref{thm:state-vs-energy} the instantaneous energy being obtained as a linear combination of the state. The state $\mathbf{q}$ mimics the original Fourier series coefficients
\begin{equation}\label{eq:state-details}\begin{split}
  \mathbf{q}_k&=\left[\begin{array}{cccccc}
    \alpha_0 & \alpha_1 & \beta_1 & \cdots & \alpha_r & \beta_r
  \end{array}\right]^T,\\
  A&=\left[\begin{array}{cccc}
    1&    &       &  \\
     & A_1&       &  \\
     &    & \ddots&  \\
     &    &       & A_r 
  \end{array}\right],\,A_n=\begin{bmatrix}0 & \frac{n}{\xi} \\ -\frac{n^2}{\xi^2} & 0\end{bmatrix},\\
  C&=\left[\begin{array}{cccccc}
    1 & 1 & 0 & \cdots & 1 & 0
  \end{array}\right],
\end{split}\end{equation}
where $\mathbf{q}_k\in\mathbb{R}^j$ given $j:=2r+1$, $A\in\mathbb{R}^{j\times j}$ is the state transmission matrix, and $C\in\mathbb{R}^j$ is the output matrix. In matrix $A$, the first value is one, $A_n$ is later on the diagonal, and zero in the remainder.

The control $\mathbf{u}$ along with the input matrix
\begin{equation}\label{eq:state-control}\begin{split}  
  \mathbf{u}_k&=\begin{bmatrix}g(\mathcal{C}_k)-g(\mathcal{C}_{k-1}) & \mathbf{c}_k-\mathbf{c}_{k-1}\end{bmatrix}^T,\\
  B&=\left[\begin{array}{cccc}
    1& \omega_{k,1}& \cdots& \omega_{k,\rho}  \\
     &            0&       &  \\
     &             & \ddots&  \\
     &             &       & 0
  \end{array}\right],
\end{split}\end{equation}
where $\mathcal{C}_k$ is defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, $\mathbf{u}_{0}=\begin{bmatrix}0 & \cdots & 0\end{bmatrix}^T$ and $B\in\mathbb{R}^{j\times l}$. Moreover, the first item is one, while the others on the first row are gain factors $\omega_{k}\in\mathbb{R}$, quantifying the contribution of a given TEE adjustment to the instantaneous energy.

The energy evolution analysis necessitates the following realistic assumption.
\begin{assm}\label{assm:periodic} 
Given two time instants $k_1,k_2\in[t_f]$ s.t. $k_1>k_2$ and a constant value $n\in\mathbb{R}_{> 0}$, there exist an arbitrary constant displacement $e\in\mathbb{R}$
\begin{equation}
  \abs{y_{k}-y_{k+n}}= e\,\,\,\forall k\in[k_1,k_2].
\end{equation}
\end{assm}
Physically, the time evolution of the instantaneous energy consumption is assumed periodic, in the sense that it presents repetitive patterns. We show in Section~\ref{sec:experimental} the assumption being eased in practice to a set $\mathbb{E}\subset\mathbb{R}$, or omitted under specific conditions.

Equation~(\ref{eq:state-control}) accounts for the energy due to the computations. The energy due to the change of TEEs parameters is merely a linear combination of the gain factor and the value of the TEE adjustment. Nevertheless, the change updates the trajectory which will hence affect the reading from the sensors and adjust the energy evolution accordingly. The linearity simulates how a variation affects the energy, for instance, a decrement in the radius of a circular TEE adds a negative contribution, thus simulates the lowering of instantaneous energy consumption.

@@

@@

The energy cost of the computations is assessed using \powprof{}, an open-source modeling tool presented in our previous work~\cite{seewald2019coarse}, that measures software configurations empirically and builds an energy model. Specifically, the tool builds a linear interpolation, one per each task. It hence requires the user to implement the mission as a ROS system with one or more ROS nodes changing the computational load by node-specific ROS parameters (QoS).

Suppose the system is composed of $\sigma$ ROS nodes. Let us define a computational control action
\begin{equation}\label{eq:qos-def}
  \mathcal{C}_k:=\left\{u:u\in\text{QoS}_{k,n}\,\,\,\forall n\in\{0,\dots,\sigma-1\},\,\forall k\in\mathbb{T}\right\},
\end{equation}
where $\text{QoS}_{k,n}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $n$-th QoS value at time instant $k$, and $\mathcal{C}_k\in\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ QoS values. Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous energy value obtained interrogating \powprof{}. The instantaneous computational energy component can be defined
\begin{equation}\label{eq:energy-comp}\begin{split}
  y_k^c:&=g\left(\text{QoS}_{k,0},\dots,\text{QoS}_{k,\sigma-1}\right)=g\left(\mathcal{C}_{k}\right).\\
\end{split}\end{equation}

The QoS parameters $\mathcal{C}_k$ can be subject to different constraints at different states. Physically, this means that the UAV can perform the ROS nodes within different QoS ranges in time while flying
\begin{equation}\label{eq:qos-lims}\begin{split}
  \underline{\text{QoS}}_{k,n}\leq \,&\text{QoS}_{k,n}\leq \overline{\text{QoS}}_{k,n},\\
  &\forall n\in\{0,\cdots,\sigma-1\},\,\forall k\in\mathbb{T},
\end{split}\end{equation}
where the values $\underline{\text{QoS}}_{k,n},\overline{\text{QoS}}_{k,n}$ are retrieved from the mission $\mathcal{M}$.

@@

>>>>

%% math package
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{arydshln}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}

\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}

@@

\renewcommand{\qedsymbol}{$\blacksquare$}

\theoremstyle{definition}
\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{assm}[thm]{Assumption}
\newtheorem{cor}{Corollary}
\newtheorem{conj}{Conjecture}[section]
\newtheorem{defn}{Definition}[section]
\newtheorem{exmp}{Example}[section]
\newtheorem{rem}{Remark}

@@

The proposed algorithm alters the energy consumption dynamically by means of mission-specific parameters: the Quality of Service (QoS) of the computations, and the trajectory-explicit equations (TEEs) adjustments. In the remainder of the paper, we strictly adopt the following notation.  We refer to the values of mission-specific QoS and TEEs parameters as computations and adjustments, to the constraints sets that delimit such computations and adjustments as QoS and TEEs sets, and to the current trajectory as TEE. Our goal is a mission extension by optimizing both computations and adjustments as the UAV flies and its batteries drain. First, the algorithm optimizes computations requiring the UAV to include robot operating system (ROS) nodes. Then, it optimizes adjustments--a way to alter the trajectory--and guides the UAV using a vector field~\cite{de2017guidance} that converges smoothly to such trajectory. It relies on the assumptions of the mission being \emph{periodic} and \emph{uncertain}. The periodicity is directly observed, by e.g., the UAV flying in repetitive patterns, and the uncertainty accounts for the environmental interference with e.g., a fixed-wing UAV drifting due to windy weather. It addresses the periodicity modeling the energy with Fourier analysis--being the mission periodic, we expect the energy to evolve also periodically--and the uncertainty with a state estimator. It selects the controls (computations and adjustments) using robust output feedback model predictive control (MPC).

In the spirit of reducing waste, costs, and resources, we showcase the algorithm using the problem of dynamic mission planning for a precision agriculture fixed-wing UAV. Such a scenario is often put into practice~\cite{hajjaj2014review} with ground mobile robots used for harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}, and UAVs for preventing damage and ensuring better crop quality~\cite{puri2017agriculture, daponte2019review}. The mission consist of a UAV flying in ellipses shifted in time, detecting obstacles using a convolutional neural network (CNN), and informing grounded mobile robots employed for future harvesting--a monitoring mission optimized for the craft's dynamics. The algorithm plans the mission controlling the processing rate and the length of the semi-major and -minor axis. Data indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest computations.

The remainder of the paper is organized as follows. The overview of dynamic mission planning is set in Section~\ref{sec:prob}, along with a suitable model for the position and energy. The algorithm that uses the model and solves the mobile robot dynamic mission planning problem is proposed in Section~\ref{sec:algo}. Section~\ref{sec:experimental} presents the result and showcase the performance. The paper finishes with some conclusions in Section~\ref{sec:conclusion}.

@@

Let the mission be a generic continuous twice differentiable TEE $\varphi$ and a set of $\sigma$ tasks $\psi_1,\dots,\psi_{\sigma}$. Moreover, let $t_f$ be the mission final time, $[\,\cdot\,]$ the set $\{1,2,\dots,\,\cdot\,\}$, and $\underline{\,\cdot\,},\overline{\,\cdot\,}$ the upper and lower bound of $\,\cdot\,$.

\begin{defn}[Mission]\label{def:mission}
  At a time instant $k\in[0,t_f)\subseteq\mathbb{R}_{\geq 0}$, the mission is defined as the ordered list
  \begin{equation}\label{eq:mission}\begin{split}
    \mathcal{M}_k:=\{(\varphi,\psi_1,...,\psi_\sigma)\mid\exists&\,\,\varphi\in\mathbb{C}_k,\,\\&\psi_i\in\mathbb{S}_{k,i}\,\forall i\in[\sigma]\},
  \end{split}\end{equation}
  where $\mathbb{C}_k:=[\underline{c}_k,\overline{c}_k]\subseteq\mathbb{R}$ is the TEEs set, and $\mathbb{S}_{k,i}:=[\underline{s}_{k,i},\overline{s}_{k,i}]\subseteq\mathbb{Z}_{\geq 0}$ the $i$-th task QoS set.
\end{defn}

The overall plan is the union of all the missions. If for simplicity the system is sampled discrete-time
\begin{equation}
  \mathcal{M}:=\bigcup_{i\in[t_f]}{\mathcal{M}_i},
\end{equation}
the algorithm inputs $\mathcal{M}$ and outputs the position and the instantaneous energy consumption, while it adapts the controls--an action performed evolving the mission state.

@@

Consider the position $\mathbf{p}\in\mathbb{R}^2$ of a UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ w.r.t. some inertial navigation frame $\mathcal{O}_W$, the set
\begin{equation}\label{eq:area}
  \mathcal{P}_k:=\{\mathbf{p}_k\mid\varphi_k(\mathbf{p}_k,c_{k,1},\dots,c_{k,\rho})\in\mathbb{C}_k\},
\end{equation}
delimits the area where the $k$-th TEE $\varphi_k:\mathbb{R}^2\times\mathbb{R}^{\rho}\rightarrow\mathbb{R}$ is free to evolve using $\rho$ adjustments $\mathbf{c}_k:=c_{k,1},...,c_{k,\rho}$, being the TEE satisfied for all the approaching points $\varphi_k\rightarrow\mathbb{C}_k$.

The algorithm uses the concept to select the adjustments s.t. $\varphi_k(\mathbf{p}_k,\mathbf{c}_k^0)$ has the highest energy value. It guides the UAV to the new position $\mathbf{p}_{k+1}$ using the vector field of $\varPhi:=\varphi_k(\mathbf{p}_k,\mathbf{c}_k^0)$, deriving the direction to follow--the desired velocity vector
\begin{equation}\label{eq:pd}
  \dot{\mathbf{p}}_d(\mathbf{p}_k):=E\nabla\varPhi-k_e\varPhi\nabla\varPhi,\,\,\,E=\begin{bmatrix}
    0&1\\-1&0
  \end{bmatrix},
\end{equation}
where $\nabla\varPhi\in\mathbb{R}^2$ is the gradient, $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence. The direction the velocity vector $\dot{\mathbf{p}}_d$ is pointing at is generally different from the course heading due to the atmospheric interference.

The algorithm models the energy using a state $\mathbf{q}\in\mathbb{R}^j$ derived from Fourier analysis (the meaning of $j$ is clarified to the reader shortly) and decompose such evolution in the energy due to the trajectory, and computations--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.

@@

Suppose uncertainty in the form of $\mathbf{w}_k\in\mathbb{R}^j,v_k\in\mathbb{R}$ accounting for the unknown state and output is not present. The non-linear model in Equation~(\ref{eq:fourier}) can be expressed using an equivalent linear discrete time-invariant state-space model
\begin{equation}\label{eq:state-perf}\begin{cases}
  \mathbf{q}_{k+1}&=A\mathbf{q}_{k}+B\mathbf{u}_{k}+\mathbf{w}_k\\
  y_k&=C\mathbf{q}_k+v_k
\end{cases},\end{equation}
where $y_k\in\mathbb{R}_{\geq 0}$ is the instantaneous energy consumption. We prove formally in the Theorem~\ref{thm:state-vs-energy} the instantaneous energy being obtained as a linear combination of the state. The state $\mathbf{q}$ mimics the original Fourier series coefficients
\begin{equation}\label{eq:state-details}\begin{split}
  \mathbf{q}_k&=\left[\begin{array}{cccccc}
    \alpha_0 & \alpha_1 & \beta_1 & \cdots & \alpha_r & \beta_r
  \end{array}\right]^T,\\
  A&=\left[\begin{array}{cccc}
    1&    &       &  \\
     & A_1&       &  \\
     &    & \ddots&  \\
     &    &       & A_r 
  \end{array}\right],\,A_n=\begin{bmatrix}0 & \frac{n}{\xi} \\ -\frac{n^2}{\xi^2} & 0\end{bmatrix},\\
  C&=\left[\begin{array}{cccccc}
    1 & 1 & 0 & \cdots & 1 & 0
  \end{array}\right],
\end{split}\end{equation}
where $\mathbf{q}_k\in\mathbb{R}^j$ given $j:=2r+1$, $A\in\mathbb{R}^{j\times j}$ is the state transmission matrix, and $C\in\mathbb{R}^j$ is the output matrix. In matrix $A$, the first value is one, $A_n$ is later on the diagonal, and zero in the remainder.

The control $\mathbf{u}$ along with the input matrix
\begin{equation}\label{eq:state-control}\begin{split}  
  \mathbf{u}_k&=\begin{bmatrix}g(\mathbf{s}_k)-g(\mathbf{s}_{k-1}) & \mathbf{c}_k-\mathbf{c}_{k-1}\end{bmatrix}^T,\\
  B&=\left[\begin{array}{cccc}
    1& \omega_{k,1}& \cdots& \omega_{k,\rho}  \\
     &            0&       &  \\
     &             & \ddots&  \\
     &             &       & 0
  \end{array}\right],
\end{split}\end{equation}
where $\mathbf{s}_k$ is defined in Subsection~\ref{sec:computations-model}, $\mathbf{u}_k\in\mathbb{R}^l$ is the control given $l:=1+\rho$, $\mathbf{u}_{0}=\begin{bmatrix}0 & \cdots & 0\end{bmatrix}^T$ and $B\in\mathbb{R}^{j\times l}$. Moreover, the first item is one, while the others on the first row are gain factors $\omega_{k}\in\mathbb{R}$, quantifying the contribution of a given adjustment to the instantaneous energy.

The energy evolution analysis necessitates the following realistic assumption.
\begin{assm}[Energy evelution periodicity]\label{assm:periodic} 
Given two time instants $k_1,k_2\in[t_f]$ s.t. $k_1>k_2$ and a constant value $n\in\mathbb{R}_{> 0}$, there exist an arbitrary constant displacement $e\in\mathbb{R}$
\begin{equation}
  \abs{y_{k}-y_{k+n}}= e\,\,\,\forall k\in[k_1,k_2].
\end{equation}
\end{assm}

Physically, the time evolution of the instantaneous energy consumption is assumed periodic, in the sense that it presents repetitive patterns. We show in Section~\ref{sec:experimental} the assumption being eased in practice to a set $\mathbb{E}\subset\mathbb{R}$, or omitted under specific conditions.

Equation~(\ref{eq:state-control}) accounts for the energy due to the computations. The energy due to the adjustments is merely a linear combination of the gain factor and the adjustment. Nevertheless, the change updates the path which will hence affect the reading from the sensors and adjust the energy evolution accordingly. The linearity simulates how a variation affects the energy, for instance, a decrement in the adjustment radius of a circle when the TEE is a circle, adds a negative contribution, thus simulates the lowering of instantaneous energy consumption.

@@

The energy cost of the computations is assessed using \powprof{}, an open-source modeling tool presented in our previous work~\cite{seewald2019coarse}, that measures software configurations empirically and builds an energy model. Specifically, the tool builds a linear interpolation, one per each task. It requires the user to implement the mission as a ROS system with one or more ROS nodes changing the computational load by node-specific ROS parameters. A way to simulate the change of the computations.

The mission $\mathcal{M}$ contains a set of ordered lists with $\sigma$ tasks each (recall Definition~\ref{def:mission}). These tasks are in fact simulated by $\sigma$ ROS nodes $\Psi(\mathbf{s}_k):=\left(\psi_1(s_{k,1}),\dots,\psi_\sigma(s_{k,\sigma})\right)$. Let us define the computations
\begin{equation}\label{eq:qos-def}
  \mathbf{s}_k:=\left\{s_{k,1},\dots ,s_{k,\sigma}\mid s_i\in\mathbb{S}_{k,i}\,\forall i\in[\sigma]\right\},
\end{equation}
where $s_{k,i}:\mathbb{Z}_{\geq 0}\rightarrow\mathbb{Z}_{\geq 0}$ returns the $i$-th computation, and $\mathbf{s}_k\in\mathbb{Z}_{\geq 0}^\sigma$ the set of $\sigma$ computations at time $k$.

Let us further define $g:\mathbb{Z}_{\geq 0}\times\mathbb{Z}_{\geq 0}\rightarrow\mathbb{R}_{\geq 0}$ as the instantaneous energy value obtained interrogating \powprof{}. The instantaneous computational energy component can be defined
\begin{equation}\label{eq:energy-comp}\begin{split}
  y_k^c:&=g\left(\text{QoS}_{k,0},\dots,\text{QoS}_{k,\sigma-1}\right)=g\left(\mathbf{s}_{k}\right).\\
\end{split}\end{equation}

@@

@@

Given mission starting point $\mathcal{M}_0$, the algorithm selects the $\mathbf{s}_k$ and $\mathbf{c}_k$ (computations and adjustments) and produce a valid state evolution
\begin{equation}\begin{split}
  \mathbf{u}:=\{(\mathbf{p}_k,\mathbf{c}_k,\mathbf{s}_k)\mid&(\varphi(\mathbf{p}_k,\mathbf{c}_k),\Psi(\mathbf{s_k}))\in\mathcal{M}_k\Longrightarrow\\
  &(\varphi(\mathbf{p}_{k+1},\mathbf{c}_{k+1}),\Psi(\mathbf{s}_{k+1}))\in\mathcal{M}_{k+1}\\
  {}&\forall k\in[t_f-1]\}.
\end{split}\end{equation}
